\bf Forecasts Reconciliation: A geometric view with new insights on bias correction.

### 2019-08-12 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
Adjusted the table in Appendix

\documentclass[12pt]{article}
\usepackage{amsmath}
\usepackage{graphicx,psfrag,epsf}
\usepackage{enumerate}
\usepackage{natbib}
\usepackage{url} % not crucial - just used below for the URL

\usepackage{amssymb, qtree, bm, multirow, textcmds, siunitx,paralist}
\usepackage{mathrsfs, float, booktabs,todonotes,amsthm, xcolor,sidenotes, caption, subcaption}

@@

	\begin{table}
		\caption {Average {MSE($\times 10^3$)} of base and reconciled point forecasts at forecasts horizons $h=1,...,6$ are presented. Bias and unbiased columns represent the results for biased-base/biased-reconciled and unbiased-base/unbiased-reconciled forecasts respectively. Comparisons can be made across biased vs unbiased forecasts as well as base vs reconciled forecasts.}
		\label{tab:Results_MSE}
		\centering\tabcolsep=0.08cm

		\resizebox{\linewidth}{!}{
		\begin{tabular}{@{}lSSSSSSSSSSSS@{}}
			\toprule
			\multicolumn{1}{c}{ } & \multicolumn{2}{c}{h=1} & \multicolumn{2}{c}{h=2} & \multicolumn{2}{c}{h=3} & \multicolumn{2}{c}{h=4} & \multicolumn{2}{c}{h=5} & \multicolumn{2}{c}{h=6} \\
			\cmidrule(lr){2-3} \cmidrule(lr){4-5} \cmidrule(lr){6-7} \cmidrule(lr){8-9} \cmidrule(lr){10-11} \cmidrule(lr){12-13}
			Method & Biased & Unbiased & Biased & Unbiased & Biased & Unbiased & Biased & Unbiased & Biased & Unbiased & Biased & Unbiased\\
			\midrule
			Base & 12.18 & 161.63 & 13.14 & 243.13 & 14.08 & 269.20 & 15.88 & 325.41 & 15.49 & 332.11 & 15.79 & 344.40\\
			\hline
			MinT(Shrink) & 10.14 & $\bm{9.96}$ & 11.47 & $\bm{10.78}$ & 12.55 & $\bm{11.94}$ & 15.53 & $\bm{14.03}$ & 14.63 & $\bm{13.46}$ & 15.28 & $\bm{13.78}$\\
			\hline
			WLS & 15.62 & 13.97 & 15.93 & 13.71 & 16.65 & 14.50 & 18.91 & 16.26 & 18.76 & 16.20 & 18.85 & 15.83\\	
			\hline
			OLS & 11.73 & 135.17 & 12.80 & 204.42 & 13.73 & 225.59 & 15.56 & 272.41 & 15.17 & 278.08 & 15.49 & 288.21\\
			\hline
			Bottom-up & 17.86 & 15.55 & 17.86 & 14.90 & 18.47 & 15.61 & 20.50 & 17.21 & 20.34 & 17.04 & 20.39 & 16.69\\

@@

	These new geometric interpretations of hierarchical forecast reconciliation facilitate extensions of the problem to a probabilistic framework. We leave this discussion into a different paper. 	
	\newpage
	\section{Appendix}

	\begin{table} 
		\caption{Geographical hierarchy of Australian tourism flow}\label{table:A1}

		\resizebox{\linewidth}{!}{
			\begin{tabular}{lllllllllll}
				\toprule
				\multicolumn{3}{c}{\textbf{Level 0 - Total}}   &  &  \multicolumn{3}{l}{\textit{Zones cont.}}   &  & \multicolumn{3}{l}{\textit{Regions cont.}} \\
				\cmidrule(lr){1-3}
				1 & {\text{Tot}} & {Australia} &  & 48  & AED & Blue Mountains && 99 & FAA & Hobert and South\\
				\cmidrule(lr){1-3}
				\multicolumn{3}{c}{\textbf{Level 1 - States}}  &  & 49  & AFA & Canberra  && 100 & FBA & East Coast\\
				\cmidrule(lr){1-3}
				2 & A & NSW 				&  & 50  & BAA & Melbourne && 101 & FBB & Launceston, Tamar \& North\\
				3 & B & Victoria 			&  & 51  & BAB & Peninsula && 102 & FCA & North West\\
				4 & C & Queensland 			&  & 52  & BAC & Geelong && 103 & FCB& Wilderness West\\
				5 & D & South Australia     &  & 53  & BBA & Western && 104 & GAA& Darwin\\
				6 & E & Western Australia   &  & 54  & BCA & Lakes && 105 & GAB& Kakadu Arnhem\\
				7 & F & Tasmania   			&  & 55  & BCB & Grippsland && 106 & GAC& Katherine Daly\\
				8 & G & Northern Territory &  &  56  & BCD & Phillip Island && 107 & GBA& Barkly\\
				\cmidrule(lr){1-3} 
				\multicolumn{3}{c}{\textbf{Level 2 - Zones}}  &  &  57  & BDA & Central Murray && 108 & GBB& Lasseter\\
				\cmidrule(lr){1-3}
				9 	& AA & Metro NSW 	  	   	&  & 58  & BDB & Goulburn && 109 & GBC& Alice Springs\\
				10 	& AB & North Coast NSW 	   	&  & 59  & BDC & High Country && 110 & GBD& MacDonnell\\
				11	& AC & South Coast NSW	   	&  & 60  & BDD & Melbourne East &&&&\\
				12	& AD & South NSW 			&  & 61  & BDE & Upper Yarra &&&& \\
				13	& AE & North NSW 			&  & 62  & BDF & Murray East &&&&\\
				14	& AC & ACT					&  & 63  & BEA & Wimmera+Mallee &&&&\\
				15	& BA & Metro VIC			&  & 64  & BEB & Western Grampians &&&&\\ 		
				16	& BB & West Coast VIC		&  & 65  & BEC & Bendigo Loddon &&&&\\
				17	& BC & East Coast VIC		&  & 66  & BED & Macedon &&&&\\ 
				18	& BC & North East VIC		&  & 67  & BEE & Spa Country &&&&\\ 
				19	& BD & North West VIC		&  & 68  & BEF & Ballarat &&&&\\
				20  & CA & Metro QLD			&  & 69  & BEG & Central Highlands &&&&\\
				21  & CB & Central Coast QLD	&  & 70  & CAA & Gold Coast &&&&\\
				22  & CC & North Coast QLD		&  & 71  & CAB & Brisbane &&&&\\
				23  & CD & Inland QLD			&  & 72  & CAC & Sunshine Coast &&&&\\
				24	& DA & Metro SA				&  & 73  & CBA & Central Queensland &&&&\\	
				25	& DB & South Coast SA		&  & 74  & CBB & Bundaberg &&&&\\	
				26	& DC & Inland SA			&  & 75  & CBC & Fraser Coast &&&&\\	
				27	& DD & West Coast SA		&  & 76  & CBD & Mackay &&&&\\

				28	& EA & West Coast WA 	& & 77  & CCA & Whitsundays &&&&\\	
				29	& EB & North WA			& & 78  & CCB & Northern &&&&\\	
				30	& EC & South WA 		& & 79  & CCC & Tropical North Queensland &&&&\\	
				31	& FA & South TAS		& & 80  & CDA & Darling Downs &&&&\\
				32	& FB & North East TAS	& & 81  & CDB & Outback &&&&\\	
				33	& FC & North West TAS	& & 82  & DAA & Adelaide &&&&\\
				34	& GA & North Coast NT	& & 83  & DAB & Barossa &&&&\\
				35	& GB & Central NT		& & 84  & DAC & Adelaide Hills &&&&\\
				\cmidrule(lr){1-3}
				\multicolumn{3}{c}{\textbf{Level 2 - Regions}} & & 85  & DBA & Limestone Coast &&&&\\
				\cmidrule(lr){1-3}
				36	& AAA & Sydney 			& 	& 86  & DBB & Fleurieu Peninsula &&&&\\
				37	& AAB & Central Coast	&	& 87  & DBC & Kangaroo Island &&&&\\
				38  & ABA & Hunter 			& 	& 88  & DCA & Murraylands &&&&\\
				39  & ABB & North Coast NSW & 	& 89  & DCB & Riverland &&&&\\
				40  & ABC & Hunter			& 	& 90  & DCC & Clare Valley &&&&\\
				41  & ACA & South Coast		& 	& 91  & DCD & Flinders Range and Outback &&&&\\
				42  & ADA & Snowy Mountains & 	& 92  & DDA & Eyre Peninsula &&&&\\
				43  & ADB & Capital Country & 	& 93  & DDB & Yorke Peninsula &&&&\\
				44  & ADC & The Murray 		& 	& 94  & EAA & Australia's Coral Coast &&&&\\
				45  & ADD & Riverina 		& 	& 95  & EAB & Experience Perth &&&&\\
				45  & AEA & Central NSW 	& 	& 96  & EAC & Australia's South West &&&&\\
				46  & AEB & New England North West &  & 97  & EBA & Australia's North West &&&&\\
				47  & AEC & Outback NSW & & 98  & ECA & Australia's Golden Outback &&&&\\
				\bottomrule
			\end{tabular}
		}
	\end{table}
	\newpage

>>>>

\documentclass[12pt]{article}
\usepackage{amsmath}
\usepackage{graphicx,psfrag,epsf}
\usepackage{enumerate}
\usepackage{natbib}
\usepackage{url} % not crucial - just used below for the URL 
\usepackage{floatpag}
\usepackage{lipsum}
\usepackage{amssymb, qtree, bm, multirow, textcmds, siunitx,paralist}
\usepackage{mathrsfs, float, booktabs,todonotes,amsthm, xcolor,sidenotes, caption, subcaption}

@@

	\begin{table}
		\caption {Average {MSE($\times 10^3$)} of base and reconciled point forecasts at forecasts horizons $h=1,...,6$ are presented. Bias and unbiased columns represent the results for biased-base/biased-reconciled and unbiased-base/unbiased-reconciled forecasts respectively. Comparisons can be made across biased vs unbiased forecasts as well as base vs reconciled forecasts.}
		\label{tab:Results_MSE}
		\centering\tabcolsep=0.08cm
		\resizebox{\linewidth}{!}{
		\begin{tabular}{@{}lSSSSSSSSSSSS@{}}
			\toprule
			\multicolumn{1}{c}{ } & \multicolumn{2}{c}{h=1} & \multicolumn{2}{c}{h=2} & \multicolumn{2}{c}{h=3} & \multicolumn{2}{c}{h=4} & \multicolumn{2}{c}{h=5} & \multicolumn{2}{c}{h=6} \\
			\cmidrule(lr){2-3} \cmidrule(lr){4-5} \cmidrule(lr){6-7} \cmidrule(lr){8-9} \cmidrule(lr){10-11} \cmidrule(lr){12-13}
			Method & Biased & Unbiased & Biased & Unbiased & Biased & Unbiased & Biased & Unbiased & Biased & Unbiased & Biased & Unbiased\\
			\midrule
			Base & 12.18 & 161.63 & 13.14 & 243.13 & 14.08 & 269.20 & 15.88 & 325.41 & 15.49 & 332.11 & 15.79 & 344.40\\
			\hline
			MinT(Shrink) & 10.14 & $\bm{9.96}$ & 11.47 & $\bm{10.78}$ & 12.55 & $\bm{11.94}$ & 15.53 & $\bm{14.03}$ & 14.63 & $\bm{13.46}$ & 15.28 & $\bm{13.78}$\\
			\hline
			WLS & 15.62 & 13.97 & 15.93 & 13.71 & 16.65 & 14.50 & 18.91 & 16.26 & 18.76 & 16.20 & 18.85 & 15.83\\	
			\hline
			OLS & 11.73 & 135.17 & 12.80 & 204.42 & 13.73 & 225.59 & 15.56 & 272.41 & 15.17 & 278.08 & 15.49 & 288.21\\
			\hline
			Bottom-up & 17.86 & 15.55 & 17.86 & 14.90 & 18.47 & 15.61 & 20.50 & 17.21 & 20.34 & 17.04 & 20.39 & 16.69\\

@@

	These new geometric interpretations of hierarchical forecast reconciliation facilitate extensions of the problem to a probabilistic framework. We leave this discussion into a different paper.

	\newpage
	\section{Appendix}
	\thisfloatpagestyle{empty}
	\input{Appendix}

	\newpage
